Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence, Arbitrary Information and Forensic Workflow

### 2009-04-03 paper/paper.tex
Added write support via http (uses PUT). Its now possible to just image directly to a http URL.

% Make sure we know its a draft for now
\usepackage{draftwatermark}
\SetWatermarkFontSize{3cm}
\usepackage{fancyvrb}
%\documentclass[12pt]{article}
\usepackage{epsfig}
\usepackage[hypertexnames=false,bookmarksopenlevel=1,bookmarksopen,bookmarksnumbered,colorlinks,plainpages=false,linktocpage,linkcolor=black,citecolor=black,filecolor=black,urlcolor=black]{hyperref}
%\usepackage{natbib}
%\pagestyle{empty}
%\psdraft
%\baselineskip=20pt %Sets line spacing to 1 unit
%\bibliographystyle{elsart-num-names}
\usepackage{cite}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1:}]}{\end{trivlist}}

@@

\subsection{Rapidly converting a set of DD images}
Many hardware devices are available to acquire hard disks in the
fields. These often produce a set of uncompressed images split at a
certain size. It is possible to construct a Map Stream which
seamlessly reassembles the logical image from all the individual disk
images. The map stream may be kept in its own volume, or appended to
one (or all) of the image fragments.

@@

\subsection{Cryptographic management of evidence}
An AFF4 archive may hold multiple encrypted volumes, each in its own
Encrypted Stream. Each of those streams is encrypted using a different
master key, and therefore can have different passphrases, and can be
assigned to different users by encrypting the master key with
different X509 certificates. Its is also possible for users to create
non-encrypted volumes within the FIF file.

>>>>

% Make sure we know its a draft for now
%\usepackage{draftwatermark}
%\SetWatermarkFontSize{3cm}
\usepackage{fancyvrb}
%\documentclass[12pt]{article}
\usepackage{epsfig}
\usepackage[hypertexnames=false,bookmarksopenlevel=1,bookmarksopen,bookmarksnumbered,colorlinks,plainpages=false,linktocpage,linkcolor=black,citecolor=black,filecolor=black,urlcolor=black]{hyperref}
%\usepackage{natbib}
%\pagestyle{empty}
%\psdraft
%\baselineskip=20pt %Sets line spacing to 1 unit
%\bibliographystyle{elsart-num-names}
\usepackage{cite}
\newenvironment{definition}[1][Definition]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1:}]}{\end{trivlist}}

@@

\subsection{Rapidly converting a set of DD images}
Many hardware devices are available to acquire hard disks in the
field. These often produce a set of uncompressed images split at a
certain size. It is possible to construct a Map Stream which
seamlessly reassembles the logical image from all the individual disk
images. The map stream may be kept in its own volume, or appended to
one (or all) of the image fragments.

@@

\subsection{Cryptographic management of evidence}
An AFF4 archive may hold multiple encrypted volumes, each in its own
Encrypted Stream. Each of those streams is encrypted using a different
master key, and therefore can have different passphrases, and can be
assigned to different users by encrypting the master key with
different X509 certificates. Its is also possible for users to create
non-encrypted volumes within the AFF4 volume.
